### 2014-06-06 related_work.tex
update on related work

\paragraph{Dynamic selection}\label{dynamic-selection}
Most recently, learnt feature and classification deployment schemes based on budget aware policies have shown how to flexibly adapt computation at test time dependent on the input and intermediate results \cite{Karayev-NIPS-2012,karayev14cvpr}. We extend these ideas to the most recent developments of CNNs for visual object detection with a focus on deployment on highly parallel GPU computing hardware. In particular, we effectively combine  dense evaluation of shared, cheap feature with a fine-grained dynamic execution policies reasoning on window proposals for more expensive features.

>>>>

\paragraph{Dynamic selection}\label{dynamic-selection}
Most recently, learnt feature and classification deployment schemes based on budget aware policies have shown how to flexibly adapt computation at test time dependent on the input and intermediate results \cite{Karayev-NIPS-2012,karayev14cvpr}. We extend these ideas to the most recent developments of CNNs for visual object detection with a focus on deployment on highly parallel GPU computing hardware. In particular, we effectively combine  dense evaluation of shared, cheap feature with a fine-grained, dynamic execution policy reasoning on window proposals for more expensive features.
